Hybrid platforms and bargaining power

### 2024-01-12 src/paper/application.tex
Fix some references

In the second stage, firms that made this investment plus the platform engage in producing and selling their respective products.
If there are $N_F$ fringe entrants along with $N_P$ platform products and $N_C$ consumers, then, as discussed previously, the total value they create together is given by $\Pi(N_P, N_F, N_C) = N_C f(N_P, N_F)$.
Finally, the platform and the entrants share this profit according to the profit sharing rule from \cref{ass:profit_sharing} or \cref{ass:profit_sharing_two_sided}, and the fringe gets $\pi_F(N_P, N_F, N_C)$.

The equilibrium number of entrants is determined by a free entry condition: in the end, the fringe firms' total profits should be equal to the aggregated investment cost.
\begin{definition}
    \label{ass:free_entry}
    Let us define a free entry equilibrium by the following conditions:
    \begin{itemize}
        \item Profits are shared according to \cref{ass:profit_sharing} (one-sided bargaining) or \cref{ass:profit_sharing_two_sided} (two-sided bargaining).
        \item Entrants make zero profits after accounting for entry costs: $\pi_F(N_P, N_F) = I_F(N_F)$.
    \end{itemize}
\end{definition}

@@

\subsection{Consumers also participate in bargaining}

@@

In this section, I describe how the profit sharing rule from \cref{sec:profit_sharing} can be derived from various cooperative games.
In each of the following subsections, I formally define a cooperative game that models the platform setting, and derive the (weighted) Shapley values of the various players.
I show that they correspond to the formulas given in \cref{sec:profit_sharing}, with a specific choice of weight functions $w_P$ and $w_F$ for each case.

>>>>

In the second stage, firms that made this investment plus the platform engage in producing and selling their respective products.
If there are $N_F$ fringe entrants along with $N_P$ platform products and $N_C$ consumers, then, as discussed previously, the total value they create together is given by $\Pi(N_P, N_F, N_C) = N_C f(N_P, N_F)$.
Finally, the platform and the entrants share this profit according to the profit sharing rule from \cref{ass:profit_sharing}, and the fringe gets $\pi_F(N_P, N_F, N_C)$.

The equilibrium number of entrants is determined by a free entry condition: in the end, the fringe firms' total profits should be equal to the aggregated investment cost.
\begin{definition}
    \label{ass:free_entry}
    Let us define a free entry equilibrium by the following conditions:
    \begin{itemize}
        \item Profits are shared according to \cref{ass:profit_sharing}.
        \item Entrants make zero profits after accounting for entry costs: $\pi_F(N_P, N_F) = I_F(N_F)$.
    \end{itemize}
\end{definition}

@@

\subsection{Consumers also participate in bargaining}
\label{sec:two_sided}

@@

In this section, I describe how the profit sharing rule from \cref{ass:profit_sharing} can be derived from various cooperative games.
In each of the following subsections, I formally define a cooperative game that models the platform setting, and derive the (weighted) Shapley values of the various players.
I show that they correspond to the formulas given in \cref{ass:profit_sharing}, with a specific choice of weight functions $w_P$ and $w_F$ for each case.
